Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-10-21 referee.tex
Formatting change (no indents in first para)

A -- 1) One of the main points of the paper is studying the multiplicity of Pop III stars in a halo. This multiplicity might be due to the fact that Pop III stars have collapsed to a BH after their lifetime and a second Pop III star could form in the same halo. This is very plausible. If several Pop III stars are found forming in the same halo at the same time, however, the employed star particle algorithm has a hard-coded length scale of 1pc in which only one star particle can be formed. I am wondering if this is an effect that is resolution dependent - do the same number of stars form if the resolution is increased and the maximum distance is decreased? Which is the motivation for the length scale of 1pc?
\end{referee}

There was an error in the original draft of our paper, stating that ``If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells." It should instead say ``within 10 pc", not ``within 1 pc". This error has been corrected.

@@

\begin{referee}
B -- 2) The authors select their haloes by the halo finding algorithm Rockstar. They should add a bit of information on that code (is it fof or subfind-like?). Also, one of their main points is to compare their work to Machacek+01. Machacek+01, however, use a different halo definition (spherical around the halo centre going out to a radius of 200 times the mean density of the Universe). How do these different halo masses compare?
\end{referee}

We have added a short description of Rockstar to Section 3.1, where it is introduced.

@@

\begin{referee}
C -- Further, it is not entirely clear why atomic cooling haloes are excluded in this analysis and if they are excluded throughout the whole paper. The exclusion of atomic cooling haloes artificially shifts the average halo mass to lower values.
\end{referee}

We apologize for not being more clear on this point.  There are seven stars that form in an atomic cooling halo but are actually hosted by a subhalo that hasn't been enriched yet. This is an interesting case within itself.  We might follow up on this object in a later study because it's outside the scope of the paper.  Because we take the parent halo mass as the host halo mass, we did not include these stars in the analysis because the parent halo mass is not representative of the cooling processes inside of the subhalo.  Because this is a rare event in our simulation (7 out of 688 Pop III stars), it does not shift the average halo mass by a significant amount.  We have added some clarifying text to the first paragraph of the Section 3.1.

\begin{referee}
D -- In addition, the authors should state the fraction of haloes that have Pop III stars forming outside the halo. The baryon fraction varies with redshift. Please give an estimate by how much this influences the halo masses used here.
\end{referee}

There are 1\% of Pop III stars that form in a halo not identified by Rockstar.  To be clear, Pop III stars should not be forming outside of halos. This small percentage of Pop III stars are forming in halos but in halos not identified by Rockstar.  We have added these details to the ``Population III Host Halo Masses" subsection.

@@

F -- The authors write that Pop III star formation is generally more massive. While a fraction of the community agrees with that, there is manifoldly cited work that finds low-mass Pop III progenitors, and the authors should not let that unmentioned, but also cite eg Stacy+16, Greif+11 and Clark+11.
\end{referee}

This is a good point about low-mass Pop III stars, and we have included these references in the introduction.

\begin{referee}
G -- The authors name a few processes for suppressing Pop III star formation. For completeness, they should also mention eg X-ray heating (citing eg Jeon+14).
\end{referee}

We now include X-ray heating in the introduction and cited Jeon et al. (2014).

\begin{referee}
H -- The authors cite the well-known study from Machacek+01. However, a more recent result would be from the study by Visbal+14, giving a lower mass limit. Since the authors find a lower mass limit than Machacek+01, it would be interesting to see how this compares to the lower mass limit from the more modern paper.
\end{referee}

We have included the $M_{\rm crit}$ function that Visbal et al. (2014) use in their study (their Equation 4) for $z=20$ as a solid purple line in Figure 10. The Visbal et al. relation give similar masses as Machacek et al. (2001).  But when we input the LW background utilized in our study, the Visbal et al. relation give higher halo masses overall when compared to Machacek et al.

@@

I -- In Wise+12, three different environment regions are picked. Please provide more description on the rare peak simulation here and discuss why this one is appropriate in this context.
\end{referee}

RP stands for the ``radiation pressure" simulation from Wise et al. (2012), not rare peak of the Renaissance Simulations (Xu et al. 2016). The simulation is the same size as ours, and contains similar physics, including the radiation pressure and soft UV background, which is why we reference it here. The differences are the inclusion of H2 self-shielding and updated cosmological parameters.

\begin{referee}
J -- The initialization at z=130 is very late. I am aware that it is impossible to repeat this simulation starting at an earlier redshift, but would advise for future work.
\end{referee}

In hindsight, we agree that we initialized the simulation too late, even with 2nd order Lagrangian perturbation theory.  The maximum baryon overdensity is 1.64$\bar{\rho}_{\rm b}$, and the maximum DM particle displacement is 2.5 $\times$ (cell width).  In future studies, we will start at earlier times when the evolution is solidly in the linear regime.  We thank the referee for pointing this out.

\begin{referee}
K -- Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
\end{referee}

We chose this metallicity threshold based on the work of Omukai et al. (2005), Schneider et al. (2006), who found that dust cooling was efficient enough above this metallicity to induce low-mass star formation. About 10\% of Pop III stars form with metallicities between zero and $5 \times 10^{-6} Z_\odot$.  Stars only obtain this extremely low (non-zero) metallicity when metal mixing is incomplete.  This usually occurs when a blastwave is mixing into a nearby halo, and the core collapses before it can fully mix.  Because of the randomness of the IMF sampling and errors from numerical diffusion and other solvers, we do not place great emphasis on stars in this metallicity range.  It is unclear what would be the actual stellar metallicity when it reaches main sequence, given our 0.1 proper pc resolution.  We have made a note of this in Section 2.2.1.

\begin{referee}
L -- What is the physical motivation for a density threshold of 1.e6/cc? Is there convergence?
\end{referee}

Our choice was motivated by both previous work and our refinement strategy rather than convergence. Previous work (e.g. O'Shea et al. 2007; Yoshida et al. 2007) and later groups (e.g. Hirano et al. 2015) have shown that the number density is $\sim 10^6 \cubecm$ at our resolution limit of $0.09$ proper pc at $z=10$.  Secondly, we chose this threshold to be similar to the density that would trigger another level of AMR past our maximum level of 12 (dx = 0.09 proper pc at $z=10$).  At these scales, the grid is primarily refined from the Jeans length criterion, which is resolved by at least 8 cells.  Solving for the density in the Jeans length equation, given a typical temperature $T=300$~K with primordial cooling and a Jeans Length of $8 \times \textrm{dx}$, we obtain a number density $n = 5.7 \times 10^4~\cubecm$.  This number density does not exactly match the chosen density criterion because some oversight when setting up the simulation.  In the case where the density SF criterion is larger than $n$, the gas will continue to condense on a faster timescale than its surroundings.  Thus we are confident that this slight mismatch does not affect our results.

@@

\begin{referee}
M -- Similarly, why do the authors chose a H2 fraction of 1.e-3? (Is is a mass fraction or a number fraction?) How many Pop III stars do not form because of this threshold?
\end{referee}

We chose this critical H$_2$ fraction to match with the values found in previous work (e.g. Yoshida et al. 2007; Omukai et al. 2010) at the density threshold of $10^6~\cubecm$.  It is a number fraction.  We have added this detail to Section 2.2.1 to reflect this detail.

@@

\begin{referee}
N -- Do the authors set fixed mass limits to the IMF and if yes, which are they?  If not, which is the highest / lowest mass they find in their random sampling?  And which fraction of the Pop III stars in the simulation end up as type II SNe / BHs / PISN?
\end{referee}

In our simulation, we consider a fixed mass limit between 1 and 300 $M_{\odot}$ of the IMF. We have added this detail in section 2.2.1.  Given this IMF, 59, 36, and 5 per cent of Pop III stars become Type II SN, black holes with no SN, and PISNe, respectively. We have added this detail to Section 2.2.1.

\begin{referee}
O -- One effect than can weaken the shielding is shifting out of the Lyman-Werner resonance lines (see Hartwig+15). I am wondering how much this would affect the study presented here.
\end{referee}

Hartwig et al. (2015) take into account the Doppler-shifting of spectral lines with an improved calculation of the column densities but use the same shielding factor as we do. They find that shielding is generally less efficient at higher temperatures. In our work, because our halos are less massive, the temperatures are typically around $10^{3}$ K, which looking at their Figure 5, lies close to the 1:1 line. The shielding factor as calculated in our work will therefore not vary significantly compared to the full treatment of the column density, so we do not expect this to be a problem.  We have added a brief desription of this effect to the \hh{} Self-Shielding section.

\begin{referee}
P -- In Figure 1, please mention in the caption or at the top / bottom of the left axis that a shielding factor of 1 corresponds to no shielding and a shielding factor of 0 corresponds to high shielding, as these nomenclatures are not immediately understandable for the reader.
\end{referee}

We thank the referee for pointing out this tricky detail, and we have added it to the caption of Figure 1.

\begin{referee}
Q -- The analytic calculation of the shielding factor is a nice property of the paper. However, assuming a constant H2 fraction seems not appropriate. Please repeat this exercise for a more realistic halo profile, which could be found in the simulations or in the literature, eg by Machacek+01 themselves.
\end{referee}

This is a good point, and the plot has been adjusted accordingly. We chose to use the \hh{} radial profiles from O'Shea and Norman (2007) because of the variety of halos and high resolution. The plot now shows that the shielding factor increases as a function of mass, since at larger radii, there is less \hh{}, resulting in a less effective \hh{} shield. The overall takeaway of the plot has not changed.

>>>>

A -- 1) One of the main points of the paper is studying the multiplicity of Pop III stars in a halo. This multiplicity might be due to the fact that Pop III stars have collapsed to a BH after their lifetime and a second Pop III star could form in the same halo. This is very plausible. If several Pop III stars are found forming in the same halo at the same time, however, the employed star particle algorithm has a hard-coded length scale of 1pc in which only one star particle can be formed. I am wondering if this is an effect that is resolution dependent - do the same number of stars form if the resolution is increased and the maximum distance is decreased? Which is the motivation for the length scale of 1pc?
\end{referee}
There was an error in the original draft of our paper, stating that ``If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells." It should instead say ``within 10 pc", not ``within 1 pc". This error has been corrected.

@@

\begin{referee}
B -- 2) The authors select their haloes by the halo finding algorithm Rockstar. They should add a bit of information on that code (is it fof or subfind-like?). Also, one of their main points is to compare their work to Machacek+01. Machacek+01, however, use a different halo definition (spherical around the halo centre going out to a radius of 200 times the mean density of the Universe). How do these different halo masses compare?
\end{referee}
We have added a short description of Rockstar to Section 3.1, where it is introduced.

@@

\begin{referee}
C -- Further, it is not entirely clear why atomic cooling haloes are excluded in this analysis and if they are excluded throughout the whole paper. The exclusion of atomic cooling haloes artificially shifts the average halo mass to lower values.
\end{referee}
We apologize for not being more clear on this point.  There are seven stars that form in an atomic cooling halo but are actually hosted by a subhalo that hasn't been enriched yet. This is an interesting case within itself.  We might follow up on this object in a later study because it's outside the scope of the paper.  Because we take the parent halo mass as the host halo mass, we did not include these stars in the analysis because the parent halo mass is not representative of the cooling processes inside of the subhalo.  Because this is a rare event in our simulation (7 out of 688 Pop III stars), it does not shift the average halo mass by a significant amount.  We have added some clarifying text to the first paragraph of the Section 3.1.

\begin{referee}
D -- In addition, the authors should state the fraction of haloes that have Pop III stars forming outside the halo. The baryon fraction varies with redshift. Please give an estimate by how much this influences the halo masses used here.
\end{referee}
There are 1\% of Pop III stars that form in a halo not identified by Rockstar.  To be clear, Pop III stars should not be forming outside of halos. This small percentage of Pop III stars are forming in halos but in halos not identified by Rockstar.  We have added these details to the ``Population III Host Halo Masses" subsection.

@@

F -- The authors write that Pop III star formation is generally more massive. While a fraction of the community agrees with that, there is manifoldly cited work that finds low-mass Pop III progenitors, and the authors should not let that unmentioned, but also cite eg Stacy+16, Greif+11 and Clark+11.
\end{referee}
This is a good point about low-mass Pop III stars, and we have included these references in the introduction.

\begin{referee}
G -- The authors name a few processes for suppressing Pop III star formation. For completeness, they should also mention eg X-ray heating (citing eg Jeon+14).
\end{referee}
We now include X-ray heating in the introduction and cited Jeon et al. (2014).

\begin{referee}
H -- The authors cite the well-known study from Machacek+01. However, a more recent result would be from the study by Visbal+14, giving a lower mass limit. Since the authors find a lower mass limit than Machacek+01, it would be interesting to see how this compares to the lower mass limit from the more modern paper.
\end{referee}
We have included the $M_{\rm crit}$ function that Visbal et al. (2014) use in their study (their Equation 4) for $z=20$ as a solid purple line in Figure 10. The Visbal et al. relation give similar masses as Machacek et al. (2001).  But when we input the LW background utilized in our study, the Visbal et al. relation give higher halo masses overall when compared to Machacek et al.

@@

I -- In Wise+12, three different environment regions are picked. Please provide more description on the rare peak simulation here and discuss why this one is appropriate in this context.
\end{referee}
RP stands for the ``radiation pressure" simulation from Wise et al. (2012), not rare peak of the Renaissance Simulations (Xu et al. 2016). The simulation is the same size as ours, and contains similar physics, including the radiation pressure and soft UV background, which is why we reference it here. The differences are the inclusion of H2 self-shielding and updated cosmological parameters.

\begin{referee}
J -- The initialization at z=130 is very late. I am aware that it is impossible to repeat this simulation starting at an earlier redshift, but would advise for future work.
\end{referee}
In hindsight, we agree that we initialized the simulation too late, even with 2nd order Lagrangian perturbation theory.  The maximum baryon overdensity is 1.64$\bar{\rho}_{\rm b}$, and the maximum DM particle displacement is 2.5 $\times$ (cell width).  In future studies, we will start at earlier times when the evolution is solidly in the linear regime.  We thank the referee for pointing this out.

\begin{referee}
K -- Why do the authors pick a non-zero metalicity threshold for Pop III star formation? How many Pop III stars form between Z=0 and Z=5e-6 Z\_sol?
\end{referee}
We chose this metallicity threshold based on the work of Omukai et al. (2005), Schneider et al. (2006), who found that dust cooling was efficient enough above this metallicity to induce low-mass star formation. About 10\% of Pop III stars form with metallicities between zero and $5 \times 10^{-6} Z_\odot$.  Stars only obtain this extremely low (non-zero) metallicity when metal mixing is incomplete.  This usually occurs when a blastwave is mixing into a nearby halo, and the core collapses before it can fully mix.  Because of the randomness of the IMF sampling and errors from numerical diffusion and other solvers, we do not place great emphasis on stars in this metallicity range.  It is unclear what would be the actual stellar metallicity when it reaches main sequence, given our 0.1 proper pc resolution.  We have made a note of this in Section 2.2.1.

\begin{referee}
L -- What is the physical motivation for a density threshold of 1.e6/cc? Is there convergence?
\end{referee}
Our choice was motivated by both previous work and our refinement strategy rather than convergence. Previous work (e.g. O'Shea et al. 2007; Yoshida et al. 2007) and later groups (e.g. Hirano et al. 2015) have shown that the number density is $\sim 10^6 \cubecm$ at our resolution limit of $0.09$ proper pc at $z=10$.  Secondly, we chose this threshold to be similar to the density that would trigger another level of AMR past our maximum level of 12 (dx = 0.09 proper pc at $z=10$).  At these scales, the grid is primarily refined from the Jeans length criterion, which is resolved by at least 8 cells.  Solving for the density in the Jeans length equation, given a typical temperature $T=300$~K with primordial cooling and a Jeans Length of $8 \times \textrm{dx}$, we obtain a number density $n = 5.7 \times 10^4~\cubecm$.  This number density does not exactly match the chosen density criterion because some oversight when setting up the simulation.  In the case where the density SF criterion is larger than $n$, the gas will continue to condense on a faster timescale than its surroundings.  Thus we are confident that this slight mismatch does not affect our results.

@@

\begin{referee}
M -- Similarly, why do the authors chose a H2 fraction of 1.e-3? (Is is a mass fraction or a number fraction?) How many Pop III stars do not form because of this threshold?
\end{referee}
We chose this critical H$_2$ fraction to match with the values found in previous work (e.g. Yoshida et al. 2007; Omukai et al. 2010) at the density threshold of $10^6~\cubecm$.  It is a number fraction.  We have added this detail to Section 2.2.1 to reflect this detail.

@@

\begin{referee}
N -- Do the authors set fixed mass limits to the IMF and if yes, which are they?  If not, which is the highest / lowest mass they find in their random sampling?  And which fraction of the Pop III stars in the simulation end up as type II SNe / BHs / PISN?
\end{referee}
In our simulation, we consider a fixed mass limit between 1 and 300 $M_{\odot}$ of the IMF. We have added this detail in section 2.2.1.  Given this IMF, 59, 36, and 5 per cent of Pop III stars become Type II SN, black holes with no SN, and PISNe, respectively. We have added this detail to Section 2.2.1.

\begin{referee}
O -- One effect than can weaken the shielding is shifting out of the Lyman-Werner resonance lines (see Hartwig+15). I am wondering how much this would affect the study presented here.
\end{referee}
Hartwig et al. (2015) take into account the Doppler-shifting of spectral lines with an improved calculation of the column densities but use the same shielding factor as we do. They find that shielding is generally less efficient at higher temperatures. In our work, because our halos are less massive, the temperatures are typically around $10^{3}$ K, which looking at their Figure 5, lies close to the 1:1 line. The shielding factor as calculated in our work will therefore not vary significantly compared to the full treatment of the column density, so we do not expect this to be a problem.  We have added a brief desription of this effect to the \hh{} Self-Shielding section.

\begin{referee}
P -- In Figure 1, please mention in the caption or at the top / bottom of the left axis that a shielding factor of 1 corresponds to no shielding and a shielding factor of 0 corresponds to high shielding, as these nomenclatures are not immediately understandable for the reader.
\end{referee}
We thank the referee for pointing out this tricky detail, and we have added it to the caption of Figure 1.

\begin{referee}
Q -- The analytic calculation of the shielding factor is a nice property of the paper. However, assuming a constant H2 fraction seems not appropriate. Please repeat this exercise for a more realistic halo profile, which could be found in the simulations or in the literature, eg by Machacek+01 themselves.
\end{referee}
This is a good point, and the plot has been adjusted accordingly. We chose to use the \hh{} radial profiles from O'Shea and Norman (2007) because of the variety of halos and high resolution. The plot now shows that the shielding factor increases as a function of mass, since at larger radii, there is less \hh{}, resulting in a less effective \hh{} shield. The overall takeaway of the plot has not changed.
